The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems

### 2011-09-29 shortRange.inhomo/writeDown/main.tex
backup

In a spacial heterogeneous system, the heterogeneity error may play a
dominate role in the simulation, (see examples in section
\ref{sec:tmp2}).  Since the mean error force can be calculated
by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
heterogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
This long-range correction works because it takes into the force
contribution outside the cut-off radius. The mean of the corrected
error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is therefore given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r),
\end{align}
containing no heterogeneity error.  It worth noticing that the mean
square error of the corrected force is nothing but the variance of the
uncorrected error force: $\langle\vert\Delta\v F_{\textrm{corr}}(\v
r)\vert^2\rangle = \textrm{Var}[\Delta\v F(\v r)]$, which contains no
heterogeneous contribution.

The idea of the long-range force correction is very similar to those
proposed in earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In these works, the density
profile is assume to varying on only one direction, and the system is
subdivided into slabs perpendicular to that direction to calculate the
energy/force correction. The advantange of the our force correction is
that it has no geometric restriction on the density profile of the
system, so can be used in a wider range of heterogeneous simulations.

@@

\subsection{Long-range pressure corrections}
% By the cut-off method, the system lost the pressure contribution from
% the particles outside the cut-off radius.  In the homogeneous systems,
% the distribution of particles is assumed to be uniform outside the
% cut-off radius, and the pressure correction is calculated by
% integrating the virial from the cut-off to infinity.

@@

\section{Simulation results and discussions}\label{sec:tmp2}

@@

The direct simulation of the liquid-vapor equilibrium is a very
typical heterogeneous system, which is widely used to study the phase
coexistence properties, for example, the equilibrium liquid and vapor
density, and the surface tension. The system studied in the present
paper contains 16,000 standard Lennard-Jones particles that are
saperated into liquid phase in the center of the box and vapor phase
surrounded, see Fig.~\ref{fig:tmp1}.  The conventional dimensionless
unit system is employed: the unit of length, energy, mass and time are
denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
\sigma\sqrt{m/\varepsilon}$), respectively.  All quantities are
written in the unitless form by adding the superscript ``$\ast$''.
For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
$P^\ast = P\cdot \sigma^3 / \epsilon$ and $\mathcal E^\ast = \mathcal
E\cdot\sigma/\varepsilon$.  The MD time step {is} $\Delta t^\ast =
0.005$. The simulations last for $3\times 10^6$ time steps. The first
$1\times 10^6$ steps are discarded. The quantities of interest are
sampled every 100 time steps. The blocking average
method~\cite{flyvbjerg1989error} is applied to estimate the
statistical uncertainty of the autocorrelated data. The NVT ensemble
is generated by the Nos\`e-Hoover thermostat~\cite{nose1984molecular,
  hoover1985canonical}.  The size of the simulation box is $L_x^\ast
\times L_y^\ast \times L_z^\ast = 150\times 21\times 21$, as shown in
Fig. \ref{fig:tmp1}. This simulation box permits a maximum cut-off
radius of $r_c^\ast = 10$, and eliminates the finite size effect
reported in literatures \cite{chen1995area, orea2005oscillatory,
  biscay2009calculation}. In all simulations, the maximum cut-off
radius considered is $10$, but the reference results for comparison
are obtained by simulations carried out in a 24,000 particles system
with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
13$.

@@

In Fig. \ref{fig:tmp4}, we present the mean error force (only $x$
component) by the red solid line. The $y$ and $z$ components are not
shown because their magnitudes are negligible.  On the left interface,
the mean error force is along the positive direction of $x$ axis,
namely poiting right.  On the right interface, the mean error force is
of the same maganitude but poiting left. Therefore, the liquid density
should be higher and the vapor density should be lower than the
corresponding uniform cut-off simulation.  The real error (in green
square) and the homogeneity error (in blue solid line) are all
presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows the
homogeneity error estimate, which implies the contribution of the
heterogeneity error is successfully removed. In the bulk liquid
region, the homogeneity error is slightly overestimated, which is the
same as the uniform and adaptive cut-off simulations.

@@

\begin{figure}
  \centering
  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
  \caption{ The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with force
    corrected by the mean error force,
    i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off radius is $r^\ast_c =
    7.5$. The $x$ component of the mean error force is presented by
    the solid red line. The green squares present the real error. The
    solid blue line presents the homogeneity error. }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
  \caption{The convergence of the equilibrium gas and liquid density
    with respect to the cut-off radius. All densities are substracted
    by the reference value, namely, the liquid and vapor density
    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
    presents the results of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (FC)
    method. }
  \label{fig:tmp5}
\end{figure}

@@

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to increasing cut-off radius. The red, green
and blue points with error bars denote the results of uniform,
adaptive and long-range force correction simulations, respectively.
In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
value measured by uniform cut-off simulation of $r_c^\ast = 13$.  The
gas densities are connected by the dashed lines, and the liquid
densities are connected by the solid lines to guide the eyes.  In
Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
points connected by the dashed lines) are presented with pressure
corrected surface tension (data points connected by solid lines) and
the reference surface tension measured by uniform cut-off simulations
at $r_c^\ast = 13$ with pressure correction.

@@

For the liquid/vapor densities, the long-range force correction method
presents a much better convergence than the uniform and adaptive
cut-off simulations. The densities perfectly converge when the cut-off
radius is equal to or larger than 5, and the convergence at a cut-off
as small as 3.5 is acceptable.  With the same cut-off radius, the
computational cost of the force correction is nearly the same as the
uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
time, the force accuracy is more than one order of maganitude better.
% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.

With long-range pressure correction, the convergence of the surface
tension of all methods are greatly improved. The discrepancy between
the corrected and uncorrected pressure is the value of the correction,
which decreases with increasing cut-off radius. However, even at
$r_c^\ast=10$, the correction is not negligible for $T^\ast = 0.70$
and $T^\ast = 0.85$. At higher temperature, the statistical
uncertainty gets larger, and better convergence is achieved at smaller
cut-off radius.

Comparing the results of the force correction method at
$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c = 7.5$, the
force accuracy of the former method is 3--5 times less than the later
(see Tab. \ref{tab:tmp1}), however, the former accuracy of the
equilibrium densities and surface tension are comparable to and
sometimes even better than the later (see Fig. \ref{fig:tmp5} and
\ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the homogeneity error and
heterogeneity error play different roles in the simulations.  The
homogeneity error is actually the variation of the corrected error
force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
implies that the corrected error force may point to any direction with
the same probability, and may be cancelled by itself in a long time
average.  The heterogeneity error, in contrast, stems from the
non-vanishing value of the mean error force, which is alway pointing
at one certain direction (the same direction as the low-to-high
density jump), and has no oppotunity to be self-cancelled.

@@

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (FC) method.
    The computational cost is the number of pairwise interaction 
    measurements performed by the program, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

@@

In this section, we test the adaptive cut-off method and the long-range force
correction method in a dynamical problem: collision of nanoscale
Lennard-Jones clusters. Two initial Lennard-Jones clusters, denoted by
$A$ and $B$, are setup in the simulation box, each of which contains
the same number of particles $N_A = N_B = 10792$, with a diameter of
$d^\ast\approx 27$. The initial velocity of the clusters are $\v u_A =
\frac12(u, 0, 0)$ and $\v u_B = -\frac12(u, 0, 0)$, see
Fig. \ref{fig:tmp7}. The impact parameter $D$ is defined by the $z$
corrdinate difference between the center of mass (COM) of the
clusters. The unitless impact factor defined by
\begin{align}
  x = \frac D d
\end{align}
is used to measure how far off-center the collision happens. If $x =
0$ the collision is head-on, while $x=1$ the collision is avoided.
Ref. \cite{kalweit2006collision} investigated a board range
combination of velocity $u$ and impact factor $x$, and identified
three major collision modes: the coalescence, the streching seperation
and the shattering. The major modes were further classified into a
series submodes. In this paper, we want to study the how the collision
properties of interests are affected by the force calculation
precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
$x = 0.6$, where the major collision mode is the coalescence, and a
poor precision of force calculation may lead to a wrong major
collision mode.

@@

In Fig. \ref{fig:tmp8} and \ref{fig:tmp9}, we present the trajectory
of COM of cluster $A$ and the COM distance between the two clusters,
respectively. Three different cut-off radii of uniform cut-off
simulation are considered. It is obvious that the trajectory of
$r_c^\ast = 2.5$ is completely wrong: two clusters seperate after
collision. The $r_c^\ast = 5.0$ trajectory is reasonably good, but the
COM distance converges only when $r_c^\ast = 7.5$. This means the
precision of force calculation is crucial in the study of collision
dynamics. Althougth the precision of the adaptive cut-off method of
$r_c^\ast = 5$ is the as uniform cut-off $r_c^\ast = 5$, the former
produce better trajectory than the later. The long-range force
correction method that gets rid of the heterogeneity error produces
correct trajectory, but the motion along the trajectory is somewhat
faster than other methods (see also the angular velocity in
Fig. \ref{fig:tmp11}).

\begin{figure}
  \centering
  \includegraphics[]{fig/trajs.eps}
  \caption{The center of mass trajectory of cluster A. Uniform cut-off
    $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off $r_c = 5.0$ and
    force correction of $r^\ast_c = 2.5$ are investigated.  The time
    interval between two neighboring squares on the trajectory is 4.
  }
  \label{fig:tmp8}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/dists.eps}
  \caption{The distance between the center of mass of cluster $A$ and
    cluster $B$ as a function of time.}
  \label{fig:tmp9}
\end{figure}

>>>>

In a spacial heterogeneous system, the heterogeneity error may play a
dominate role in the simulation, (see examples in section
\ref{sec:tmp2}).  Since the mean error force can be calculated
by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
heterogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
is also refered as \emph{correction force} in the context of
long-range force correction. This correction works because it takes
into the force contribution outside the cut-off radius. The mean of
the corrected error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r),
\end{align}
containing no heterogeneity error.  It worth noticing that the mean
square error of the corrected force is nothing but the variance of the
uncorrected error force: $\langle\vert\Delta\v F_{\textrm{corr}}(\v
r)\vert^2\rangle = \textrm{Var}[\Delta\v F(\v r)]$, which contains no
heterogeneous contribution.

The idea of the long-range force correction is very similar to those
proposed by earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In these works, the density
profile is assumed varying on only one direction, and the system is
subdivided into slabs perpendicular to that direction to calculate the
energy/force correction. The advantange of the our force correction is
that it has no geometric restriction on the density profile of the
system, so can be used in a wider range of heterogeneous simulations.

@@

\subsection{Long-range pressure correction}
% By the cut-off method, the system lost the pressure contribution from
% the particles outside the cut-off radius.  In the homogeneous systems,
% the distribution of particles is assumed to be uniform outside the
% cut-off radius, and the pressure correction is calculated by
% integrating the virial from the cut-off to infinity.

@@

\section{Testing simulations and discussions}\label{sec:tmp2}

@@

The direct simulation of the liquid-vapor equilibrium is a very
typical heterogeneous system, which is widely used to study the phase
coexistence properties, for example, the equilibrium liquid/vapor
density, and the surface tension. The system studied in the present
paper contains 16,000 standard Lennard-Jones particles that are
saperated into liquid phase in the center of the box and vapor phase
surrounded, see Fig.~\ref{fig:tmp1}.  The conventional dimensionless
unit system is employed: the unit of length, energy, mass and time are
denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
\sigma\sqrt{m/\varepsilon}$), respectively.  All quantities are
written in the unitless form by adding the superscript ``$\ast$''.
For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
$P^\ast = P\cdot \sigma^3 / \epsilon$ and $\mathcal E^\ast = \mathcal
E\cdot\sigma/\varepsilon$.  The MD time step {is} $\Delta t^\ast =
0.005$. The simulations last for $3\times 10^6$ time steps. The first
$1\times 10^6$ steps are discarded. The quantities of interest are
sampled every 100 time steps. The blocking average
method~\cite{flyvbjerg1989error} is applied to estimate the
statistical uncertainty of the autocorrelated data with 95\%
confidence level. The NVT ensemble is generated by the Nos\`e-Hoover
thermostat~\cite{nose1984molecular, hoover1985canonical}.  The size of
the simulation box is $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 21\times 21$, which permits a maximum cut-off radius of
$r_c^\ast = 10$, and eliminates the finite size effect reported in
literatures \cite{chen1995area, orea2005oscillatory,
  biscay2009calculation}. In all simulations, the maximum cut-off
radius considered is $10$, but the reference results for comparison
are obtained by simulations carried out in a 24,000 particles system
with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
13$.

@@

In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
component) by the red solid line. The $y$ and $z$ components are not
shown because their magnitudes are negligible.  On the left interface,
the correction force is along the positive direction of $x$ axis,
namely poiting right.  On the right interface, the correction force is
of the same maganitude but poiting left. Therefore, the liquid density
should be higher and the vapor density should be lower than the
corresponding uniform cut-off simulation.  The real error (in green
square) and the estimated homogeneity error (in blue solid line) are
all presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows
the homogeneity error across the simulation region, which implies the
contribution of the heterogeneity error is successfully removed, or is
at least negligible. In the bulk liquid region, the homogeneity error
is slightly overestimated, which is the same as the uniform and
adaptive cut-off simulations.

@@

\begin{figure}
  \centering
  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
  \caption{ The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with long-range
    force correction, i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off
    radius is $r^\ast_c = 7.5$. The $x$ component of the correction
    force is presented by the solid red line. The green squares
    present the real error. The solid blue line presents the estimated
    homogeneity error. }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
  \caption{The convergence of the equilibrium gas and liquid density
    with respect to the cut-off radius. All densities are substracted
    by the reference value, namely, the liquid and vapor density
    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
    presents the results of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
    method. }
  \label{fig:tmp5}
\end{figure}

@@

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to increasing cut-off radius. The red, green
and blue points with error bars denote the results of uniform,
adaptive and long-range force correction, respectively.
In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
gas densities are connected by the dashed lines, and the liquid
densities are connected by the solid lines to guide the eyes.  In
Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
points connected by the dashed lines) are presented with pressure
corrected surface tension (data points connected by solid lines) and
the reference surface tension measured by uniform cut-off simulations
at $r_c^\ast = 13$ with pressure correction.

@@

For the liquid/vapor densities, the long-range force correction method
presents a much better convergence than the uniform and adaptive
cut-off simulations. The properties perfectly converge when the cut-off
radius is equal to or larger than 5, and the convergence at a cut-off
as small as 3.5 is acceptable.  With the same cut-off radius, the
computational cost of the force correction is nearly the same as the
uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
time, the force accuracy is more than one order of maganitude better.
% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.

With the long-range pressure correction, the convergence of the
surface tension of all methods are greatly improved. The discrepancy
between the corrected and uncorrected pressure is the value of the
correction, which decreases with increasing cut-off radius. However,
even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
uncertainty gets larger, and better convergence is achieved at smaller
cut-off radius.

Comparing the results of the force correction method at
$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
force accuracy of the former method is 3--5 times worse than the later
(see Tab. \ref{tab:tmp1}), however, the
density and surface tension accuracies are comparable to and
sometimes even better than the later (see Fig. \ref{fig:tmp5} and
\ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the above observation
indicates different errors play different roles in the simulations.
The homogeneity error is actually the variation of the corrected error
force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
implies that the corrected error force may point to any direction with
the same probability, and may be cancelled by itself in a long time
average.  The heterogeneity error, in contrast, stems from the
non-vanishing value of the mean error force, which is alway pointing
at one certain direction (the same direction as the low-to-high
density jump), and has no oppotunity to be self-cancelled.

@@

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the long-range
    force correction (LFC) method.
    The computational cost is the number of pairwise interaction 
    measurements, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

@@

In this section, we test the adaptive cut-off method and the long-range force
correction method in a dynamical problem: collision of nanoscale
Lennard-Jones clusters. Two initial Lennard-Jones clusters, denoted by
$A$ and $B$, are setup in the simulation box, each of which contains
the same number of particles $N_A = N_B = 10792$, with a diameter of
$d^\ast\approx 27$. The initial velocity of the clusters are $\v u_A =
\frac12(u, 0, 0)$ and $\v u_B = -\frac12(u, 0, 0)$, see
Fig. \ref{fig:tmp7}. The impact parameter $D$ is defined by the $z$
corrdinate difference between the center of mass (COM) of the
clusters. The unitless impact factor defined by
\begin{align}
  x = \frac D d
\end{align}
is used to measure how far off-center the collision happens. If $x =
0$ the collision is head-on, while $x=1$ the collision is avoided.
Ref. \cite{kalweit2006collision} investigated a board range
combination of the velocity $u$ and impact factor $x$, and identified
three major collision modes: the coalescence, the streching seperation
and the shattering. The major modes were further classified into a
series submodes. In this paper, we want to study the how the collision
properties are affected by the force 
precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
$x = 0.6$, where the major collision mode is the coalescence, and a
poor precision of force calculation may lead to a wrong major
collision mode.

@@

In Fig. \ref{fig:tmp8} and \ref{fig:tmp9}, we present the trajectory
of COM of cluster $A$ and the COM distance between the two clusters,
respectively. Three different cut-off radii of uniform cut-off
simulation are considered. It is obvious that the trajectory of
$r_c^\ast = 2.5$ is completely wrong: two clusters seperate after
collision. The $r_c^\ast = 5.0$ trajectory is reasonably good, but the
COM distance converges only when $r_c^\ast = 7.5$. This means the
precision of force calculation is crucial in the study of collision
dynamics. Althougth the precision of the adaptive cut-off method with
$r_c^\ast = 5$ is the same as uniform cut-off $r_c^\ast = 5$, the former
produces better trajectory. The long-range force
correction method that gets rid of the heterogeneity error also produces
correct trajectory, but the motion along the trajectory is somewhat
faster than other methods (see also the angular velocity in
Fig. \ref{fig:tmp11}).

\begin{figure}
  \centering
  \includegraphics[]{fig/trajs.eps}
  \caption{The center of mass trajectory of cluster A. Uniform cut-off
    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
    investigated.  The time interval between two neighboring squares
    on the trajectory is 4.  }
  \label{fig:tmp8}
\end{figure}
